Resiliencia de *Quercus pyreancia* a dos eventos de sequía

### 2017-11-08 man/ms_0_intro.Rmd
update pres and intro

@@

>>>>

* ojo hablar de que la sequía es un proceso natural, pero que se está viendo aumentado en los últimos años:

Drought is a natural phenomenon that occurs when water availability is significantly below normal levels over a long period and the supply cannot meet the existing demand.

> ver intro Ecosphere:
> Drought affects ecological systems across every climatic zone worldwide and is exacerbated by climate change and increasing anthropogenic water demands (Mishra and Singh 2010). Characterized by below-normal precipitation (Dai 2011), meteorological drought results from complex interactions between the atmosphere and hydrologic processes within the biosphere. Unlike aridity, which is a permanent feature of climate (Wilhite 1992), drought is a temporary extreme event (Palmer 1965, Mishra and Singh 2010) that can persist for extended time periods (months to years; Mishra and Singh 2010). Drought can cause significant changes in ecosystem productivity and water dynamics, and it is one of the most economically and ecologically disruptive extreme events affecting millions of people globally (Dai 2011).

@@

Climate change projections indicate that extreme events will become more common in the future (IPCC 2013), making it important that we understand how ecosystems respond to these events and the potential feedbacks to radiative forcing.

### 2017-11-08 pres/state_ms.Rmd
update pres and intro

- Item 1 
    - sub

@@

- SPEI (Standardised Precipitation-Evapotranspiration Index) para datos

@@

- Escala regional: exploramos la sequía a escala regional utilizando datos del [SPEI Global Drought Monitor](http://sac.csic.es/spei/database.html) para Sierra Nevada (spatial resolution of 0.5º) Ver [esto](https://github.com/ajpelu/qpyr_resilience/blob/master/analysis/drought/explore_drought_spei_regional.md):

## Including Plots

You can also embed plots, for example:

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

@@

- SPEI (Standardised Precipitation-Evapotranspiration Index) para datos regionales y locales
- Precipitación acumulada del año hidrológico en curso 
- Long term (>1950) y short-term (>2000)

@@

- Escala **regional**:
    - Datos de [\textcolor{blue}{SPEI Global Drought Monitor}](http://sac.csic.es/spei/database.html) para Sierra Nevada (spatial resolution of 0.5º) Ver [\textcolor{blue}{esto}](https://github.com/ajpelu/qpyr_resilience/blob/master/analysis/drought/explore_drought_spei_regional.md)

- Escala **local**:
    - Calcular datos SPEI para tres estaciones de la [\textcolor{blue}{red RIA}](http://www.juntadeandalucia.es/agriculturaypesca/ifapa/ria/servlet/FrontController) durante el periodo 2000 - 2016: [\textcolor{blue}{Cadiar}](http://www.juntadeandalucia.es/agriculturaypesca/ifapa/ria/servlet/FrontController?action=Static&url=coordenadas.jsp&c_provincia=18&c_estacion=7), [\textcolor{blue}{Padul}](http://www.juntadeandalucia.es/agriculturaypesca/ifapa/ria/servlet/FrontController?action=Static&url=coordenadas.jsp&c_provincia=18&c_estacion=10) y [\textcolor{blue}{Jerez del Marquesado}](http://www.juntadeandalucia.es/agriculturaypesca/ifapa/ria/servlet/FrontController?action=Static&url=coordenadas.jsp&c_provincia=18&c_estacion=6)
    - Curvas de precipitación acumulada RIA y datos base Aérea (obtenidos de la REDIAM) (desde 1950) 
    - Ver [\textcolor{blue}{flexdashboard drought}](https://rawgit.com/ajpelu/qpyr_dendro/master/analysis/drought/drought_dashboard.html)

![](../analysis/drought/explore_drought_spei_regional_files/figure-markdown_github/plot_spei1970-1.png)

- Para la caracterización de los dos periodos de sequía ¿Incluir alguna referencia a estos análisis (quizá como *supplementary materials*) o solamente referencias bibliofrágicas?

Aquí deberíamos incluir los objetivos del paper y las preguntas

# References
